\section{Conclusion}

This paper develops a semiparametric framework in which a WGAN-GP learns a
latent valuation distribution and a cross-fitted score targets a regularized
auction policy parameter. For a fixed bandwidth, orthogonality, cross-fitting,
local $o(n^{-1/4})$ nuisance accuracy, and root regularity yield asymptotic
linearity and valid inference for the regularized reserve. The Monte Carlo
study delivers a deliberately cautionary result:
good global fit and formal Neyman orthogonality do not ensure valid inference
when the reserve depends on a weakly observed tail and the local nuisance error
remains large. Fold averaging is accurate in the baseline design, while the
WGAN-based influence correction overadjusts and its nominal intervals
undercover. An oracle and empirical-local ablation changes the conclusion from
a generic failure to a precise design recommendation: training-fold local
moments attain near-oracle RMSE and coverage, so WGAN-GP should estimate the
global structural distribution while a dedicated observable local learner
supplies the reserve score. Shrinking-bandwidth theory and conditional local
nuisances remain necessary before taking this hybrid to an empirical auction
application. An external-validity design shows that this conclusion is not
specific to the baseline lognormal distribution: for three or five bidders,
fixed-bandwidth target coverage remains between 92.0 and 96.5 percent across
baseline, heavy-tail, and mixture distributions. With ten bidders, however,
almost no auction maxima lie near the reserve at the smaller sample size;
coverage falls to about 78 percent and multiple roots emerge. This identifies
a sharper boundary for the method: orthogonality protects against nuisance
estimation error but cannot replace local identifying information absent from
the observed order statistic. The first bandwidth-path experiment also cautions against treating
undersmoothing as automatic bias removal: slower paths retain regularization
bias, while faster paths create multiple roots and high variance. The current
credible claim is valid fixed-bandwidth inference for a regularized reserve. A
covariance-aware Richardson correction on the stable $n^{-0.2}$ path materially
reduces exact-target bias and RMSE and raises coverage, but does not fully
restore the nominal level. A three-bandwidth residual-bias envelope raises
exact-reserve coverage to 96.5 percent throughout that path. Enumerating and
uniting all continuation-root intervals does not further change coverage, but
becomes very costly under aggressive undersmoothing. This locates the stable-
path failure in residual smoothing bias rather than root omission and provides
a useful exact-target prototype. It remains a diagnostic confidence set rather
than a uniform theorem, so the fixed-bandwidth regularized target is still the
paper's strongest formally justified inferential claim.
