\section{WGAN-GP Nuisance Estimation}

For the baseline implementation, the generator maps independent bidder-level
noise into a log valuation:
\begin{equation}
\widetilde L_{ij}=G_{\gamma}(Z_{ij}),\qquad
\widetilde V_{ij}=\exp(\widetilde L_{ij}),
\qquad Z_{ij}\overset{\mathrm{iid}}{\sim}\mathcal N(0,I).
\end{equation}
The same scalar generator is called independently for every bidder. This is
essential: a network that produces the entire bidder vector from one common
noise draw generally induces dependence across values and violates the
independent-private-values benchmark. Synthetic observables are constructed
using the same order-statistic map as the data,
\begin{equation}
\log\widetilde B_j=\max_{1\leq i\leq N}\widetilde L_{ij}.
\end{equation}
A critic compares standardized real and synthetic log maxima. Gradient-penalty
regularization imposes an approximate Lipschitz restriction on the critic. In
the pilot, each network has two hidden layers with 64 units, the bidder-level
noise dimension is eight, and every generator update follows five critic
updates. Checkpoints are selected using only the empirical Wasserstein distance
between real and generated maxima; the true reserve is not used in training or
model selection.

The trained generator induces estimates of the latent distribution, revenue
curve, and other nuisance functions required by the reserve-price score. The
full DML procedure will repeat nuisance training separately within each
training fold and will evaluate the reserve score only on the corresponding
held-out fold.

As a computational precursor, I also report a fold-averaged plug-in. Partition
the auctions into $K$ folds and train $\widehat F^{(-k)}$ outside fold $k$.
Define
\begin{equation}
\widehat r^{(-k)}_{\mathrm{PI}}
\in\arg\max_r r\{1-\widehat F^{(-k)}(r)\},
\qquad
\overline r_{\mathrm{FA}}=\frac{1}{K}\sum_{k=1}^K
\widehat r^{(-k)}_{\mathrm{PI}}.
\end{equation}
This construction measures the stability gained from sample splitting and
averaging independently trained generators. Because the held-out observations
do not yet enter an observation-level reserve score, $\overline r_{\mathrm{FA}}$
is not the orthogonal DML estimator.
