\section{Cross-Fitted Orthogonal Estimation}

Partition the auction sample into folds $I_1,\ldots,I_K$. For each fold $k$,
train the WGAN-GP and estimate all nuisance functions using observations outside
$I_k$. Denote the resulting nuisance estimate by $\widehat\eta^{(-k)}$.

Sample splitting by itself is not sufficient for DML in this application. The
fold-averaged plug-in $\overline r_{\mathrm{FA}}$ introduced in Section~5 uses
the same training partitions but does not evaluate an observation-level score
on $I_k$. It is therefore an ensemble benchmark. Cross-fitting acquires its
inferential role only when each held-out observation enters the score below.

Let $\Phi$ and $\phi$ denote the standard normal CDF and density. For fixed
bandwidth $h$, define the observable signals
\begin{equation}
S_h(B;\theta)=\Phi\!\left(\frac{\theta-B}{h}\right),
\qquad
K_h(B;\theta)=\frac{1}{h}\phi\!\left(\frac{\theta-B}{h}\right),
\end{equation}
and the local nuisance vector
$\eta_h(\theta)=(A_h(\theta),G_h(\theta))$, where
$A_h(\theta)=\mathbb E[S_h(B;\theta)]$ and
$G_h(\theta)=\mathbb E[K_h(B;\theta)]$. The regularized reserve moment is
\begin{equation}
m_h(\theta,A,G)=1-A^{1/N}-\frac{\theta}{N}A^{1/N-1}G.
\label{eq:regularized-reserve-moment}
\end{equation}
The fixed-bandwidth target $\theta_{0,h}$ is the selected zero of
$m_h(\theta,A_h(\theta),G_h(\theta))$. It need not equal the exact Myerson
reserve $r_0$; approximation of $r_0$ requires a separate shrinking-bandwidth
argument.

The derivatives needed for the locally robust correction are
\begin{align}
m_A(\theta,A,G)
&=-\frac{1}{N}A^{1/N-1}
-\frac{\theta}{N}\left(\frac{1}{N}-1\right)A^{1/N-2}G,\\
m_G(\theta,A,G)&=-\frac{\theta}{N}A^{1/N-1}.
\end{align}
The observation-level score is
\begin{equation}
\begin{split}
\psi_h(B;\theta,A,G)
={}&m_h(\theta,A,G)
+m_A(\theta,A,G)\{S_h(B;\theta)-A\}\\
&+m_G(\theta,A,G)\{K_h(B;\theta)-G\}.
\end{split}
\label{eq:orthogonal-reserve-score}
\end{equation}
Because the two residuals have mean zero at the truth, differentiation of the
score expectation adds $-m_A$ and $-m_G$ to the derivatives of the first term.
Hence
\begin{equation}
\left.\partial_{(A,G)}
\mathbb E\left[\psi_h(B;\theta_{0,h},A,G)\right]
\right|_{(A,G)=\eta_{0,h}(\theta_{0,h})}=0.
\end{equation}

The estimator solves
\begin{equation}
\frac{1}{n}\sum_{k=1}^K\sum_{i\in I_k}
\psi_h\!\left(B_i;\widehat\theta_h,
\widehat A_h^{(-k)}(\widehat\theta_h),
\widehat G_h^{(-k)}(\widehat\theta_h)\right)=0.
\end{equation}

For a formal fixed-bandwidth statement, write
$\eta_h(\theta)=(A_h(\theta),G_h(\theta))$ and
$\Psi_h(\theta,\eta)=\mathbb E[\psi_h(B;\theta,\eta(\theta))]$.

\begin{assumption}[Fixed-bandwidth regularity]
\label{ass:fixed-h}
For fixed $h>0$: (i) the auctions are i.i.d.; (ii) $\theta_{0,h}$ is an
interior, locally unique zero of $\Psi_h(\theta,\eta_{0,h})$, the map is
differentiable in $\theta$, and
$J_h=\partial_\theta\Psi_h(\theta_{0,h},\eta_{0,h})$ is bounded away from zero;
(iii) conditional on each training sample, the held-out score observations are
independent of $\widehat\eta_h^{(-k)}$, and for a neighborhood $\mathcal N_h$,
\begin{equation}
\max_{k\leq K}\sup_{\theta\in\mathcal N_h}
\|\widehat\eta_h^{(-k)}(\theta)-\eta_{0,h}(\theta)\|
=O_p(\rho_n),\qquad \rho_n=o(n^{-1/4});
\end{equation}
(iv) the score is twice continuously differentiable in the local nuisance with
bounded second derivative on that neighborhood and has a uniformly bounded
$2+\delta$ moment for some $\delta>0$, with score variance bounded away from
zero; and (v) the selected empirical root and
the numerical Jacobian are consistent for $\theta_{0,h}$ and $J_h$.
The nuisance rate includes both WGAN estimation error and finite synthetic-
sample error.
\end{assumption}

\begin{theorem}[Fixed-bandwidth DML inference]
\label{thm:fixed-h-dml}
Under Assumption~\ref{ass:fixed-h},
\begin{equation}
\sqrt n(\widehat\theta_h-\theta_{0,h})
=\frac{1}{\sqrt n}\sum_{i=1}^n\varphi_{i,h}+o_p(1),
\qquad
\varphi_{i,h}=-J_h^{-1}
\psi_h(B_i;\theta_{0,h},\eta_{0,h}),
\label{eq:fixed-h-linearization}
\end{equation}
and the studentized statistic converges to a standard normal distribution.
The empirical influence-function variance is consistent. Consequently, the
usual Wald interval has asymptotic coverage $1-\gamma$ for the regularized
target $\theta_{0,h}$.
\end{theorem}

Theorem~\ref{thm:fixed-h-dml} is deliberately about $\theta_{0,h}$, not $r_0$.
Orthogonality makes the nuisance contribution second order, so the sufficient
$o(n^{-1/4})$ local rate controls the remainder. It does not follow from a
small global Wasserstein distance. The Monte Carlo ablations below measure
whether this sufficient local approximation is credible for each nuisance
learner.
Here the fold-specific nuisances are computed from maximum bids simulated by
the WGAN trained outside fold $k$. A numerical derivative of the cross-fitted
mean score estimates the Jacobian, and the empirical score variance supplies
the conventional influence-function standard error. Validity still requires
the second-order nuisance remainder and generator simulation error to be
smaller than sampling error. The pilot below directly tests, rather than
assumes, this requirement.

To diagnose a failure of the WGAN-based nuisance, I also evaluate two versions
of the identical score. The empirical-local version replaces generated maxima
with observed maxima from the corresponding training fold when estimating
$(A_h,G_h)$. The oracle version supplies their population values from the known
Monte Carlo DGP. Agreement between these two versions, together with failure of
the WGAN version, isolates the problem in nuisance approximation rather than in
equation~\eqref{eq:orthogonal-reserve-score}.

Inference for the exact reserve adds a separate bandwidth problem. Under local
smoothness, Gaussian regularization produces a leading approximation bias of
order $h^2$, while the density component of the score has stochastic scale of
order $(nh)^{-1/2}$. A heuristic undersmoothing requirement is therefore
$nh^5\to0$, together with $nh\to\infty$. For a power rule $h_n\propto
n^{-\alpha}$, this suggests $1/5<\alpha<1$. These rate inequalities do not
guarantee stable finite-sample root selection, especially because the maximum-
bid CDF is small near the reserve. The simulation below reports both coverage
of $\theta_{0,h_n}$ and coverage of $r_0$ rather than treating them as the same
target.

To remove the leading smoothing bias without forcing $h_n$ into the unstable
region, suppose the selected population root admits the local expansion

\begin{equation}
\theta_{0,h}=r_0+b_2h^2+O(h^4).
\end{equation}

For a fixed ratio $\lambda>1$, define the Richardson estimator

\begin{equation}
\widehat r_{\mathrm R}
=\frac{\lambda^2\widehat\theta_h-
\widehat\theta_{\lambda h}}{\lambda^2-1}.
\label{eq:richardson-reserve}
\end{equation}

The $O(h^2)$ term cancels in its population analogue. Both estimates use the
same folds and observations, so their dependence must enter inference. If
$\widehat\varphi_{i,h}$ and $\widehat\varphi_{i,\lambda h}$ are their estimated
influence values, the corrected influence value is

\begin{equation}
\widehat\varphi_{i,\mathrm R}
=\frac{\lambda^2\widehat\varphi_{i,h}-
\widehat\varphi_{i,\lambda h}}{\lambda^2-1},
\qquad
\widehat{\mathrm{se}}(\widehat r_{\mathrm R})
=\frac{\widehat{\mathrm{sd}}(\widehat\varphi_{i,\mathrm R})}{\sqrt n}.
\end{equation}

The implementation sets $\lambda=\sqrt{2}$, so
$\widehat r_{\mathrm R}=2\widehat\theta_h-
\widehat\theta_{\sqrt{2}h}$. It selects the smoother root first and uses it as
the reference for the smaller-bandwidth root. This continuation rule reduces
arbitrary root switching but does not eliminate multiple-root uncertainty.

\begin{proposition}[Exact-reserve Richardson inference]
\label{prop:richardson-exact}
Let $h_n\to0$ and fix $\lambda>1$. Suppose the roots at $h_n$ and
$\lambda h_n$ satisfy a joint version of
equation~\eqref{eq:fixed-h-linearization}, their covariance estimator is
consistent, the relevant population roots are locally unique and separated,
and
\begin{equation}
\theta_{0,h}=r_0+b_2h^2+b_4h^4+o(h^4).
\end{equation}
If $s_{\mathrm R,n}^2$ is the variance of the Richardson influence value and
\begin{equation}
\frac{\sqrt n h_n^4}{s_{\mathrm R,n}}\to0,
\label{eq:richardson-rate}
\end{equation}
then the covariance-aware Richardson statistic, centered at $r_0$ and divided
by $s_{\mathrm R,n}/\sqrt n$, converges to a standard normal distribution.
When $s_{\mathrm R,n}\asymp h_n^{-1/2}$, a sufficient bandwidth condition is
$nh_n\to\infty$ and $nh_n^9\to0$.
\end{proposition}

Proposition~\ref{prop:richardson-exact} isolates what the finite-sample
experiment must check: local nuisance rates along the bandwidth path, root
separation, covariance across bandwidths, and residual bias relative to the
standard error. Proofs are in the appendix.

The remaining $O(h^4)$ term can be diagnosed with a third bandwidth. Strengthen
the local expansion to
\begin{equation}
\theta_{0,h}=r_0+b_2h^2+b_4h^4+O(h^6)
\end{equation}
and let $\widehat r_{\mathrm R}(h)$ denote
equation~\eqref{eq:richardson-reserve}. The adjacent extrapolation is
$\widehat r_{\mathrm R}(\lambda h)$, constructed from $\lambda h$ and
$\lambda^2h$. Since
\begin{equation}
r_{\mathrm R}(\lambda h)-r_{\mathrm R}(h)
=(\lambda^4-1)\{r_{\mathrm R}(h)-r_0\}+O(h^6),
\end{equation}
the absolute residual-bias diagnostic is
\begin{equation}
\widehat B_h=
\frac{|\widehat D_h|+1.96\,\widehat{\mathrm{se}}(\widehat D_h)}
{\lambda^4-1},
\qquad
\widehat D_h=\widehat r_{\mathrm R}(\lambda h)
-\widehat r_{\mathrm R}(h).
\label{eq:residual-bias-bound}
\end{equation}
The standard error of $\widehat D_h$ again combines observation-level
influence values across all three bandwidths and therefore retains their
covariance. I report the bias-envelope interval
\begin{equation}
\left[\widehat r_{\mathrm R}(h)-1.96\widehat{\mathrm{se}}_{\mathrm R}
-\widehat B_h,\;
\widehat r_{\mathrm R}(h)+1.96\widehat{\mathrm{se}}_{\mathrm R}
+\widehat B_h\right].
\label{eq:bias-envelope}
\end{equation}

For root robustness, I enumerate every grid crossing at $h$, connect each to
the nearest root at $\lambda h$ and then $\lambda^2h$, construct
equation~\eqref{eq:bias-envelope} for every continuation chain, and take the
union of those intervals. This retains disconnected components rather than
silently selecting one root. The procedure is a finite-sample diagnostic, not
an honest uniform confidence set: its interpretation requires a stable even-
order bias expansion, adequate grid coverage, and reliable local Gaussian
approximations along each root chain.
