\section{Related Literature}

The starting point is the virtual-value characterization of optimal reserves
in \citet{myerson1981}. The observation model belongs to the order-statistics
literature surveyed by \citet{atheyhaile2007}: under symmetric independent
private values and known competition, the distribution of the observed maximum
identifies the latent valuation distribution. \citet{menzelmorganti2013}
develop large-sample theory for auction estimators based on order statistics.
Relative to direct inversion, the present paper asks whether a structural
generator can regularize the latent distribution while preserving inference
on one economically important functional. The weakly observed lower tail of
the maximum distribution is central rather than incidental to that comparison.

The computational component builds on Wasserstein generative adversarial
networks \citep{arjovsky2017} and gradient-penalty training
\citep{gulrajani2017}. It is also related to adversarial structural estimation,
which embeds economic restrictions and a simulator inside a distribution-
matching problem \citep{kaji2026}. Here the restriction is imposed before the
observable is formed: independent bidder-level draws are mapped into auction
maxima. The main diagnostic result is that good fit of this observable
distribution does not guarantee the local CDF and density accuracy needed by
the reserve score.

Finally, the inference layer follows the cross-fitting and orthogonality logic
of double machine learning \citep{chernozhukov2018}. The target differs
from standard treatment-effect and regression examples in two ways. It is an
implicit nonlinear policy functional of a latent distribution, and its
regularized score contains a density component whose variance changes with the
bandwidth. The paper therefore separates three claims that are often combined:
inference for a fixed regularized root, approximation of the exact Myerson
reserve as the bandwidth shrinks, and root-robust inference when the empirical
moment is nonmonotone.
