\documentclass[11pt]{article}
\usepackage[margin=0.72in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

\definecolor{heading}{RGB}{28,67,110}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}
\setlength{\leftmargini}{1.3em}
\setlength{\leftmarginii}{1.2em}
\newcommand{\memoheading}[1]{\vspace{3pt}{\color{heading}\bfseries #1}\par}

\begin{document}

\begin{center}
{\Large\bfseries Adviser Review Memo}\par
\vspace{2pt}
{\large Semiparametric Estimation of Myerson Reserve Prices with WGAN-GP and DML}\par
\vspace{2pt}
Shunyu Hao \hfill July 19, 2026
\end{center}

\memoheading{Decision requested}
I would like guidance on whether the current methodological and Monte Carlo
paper is ready for a computational-econometrics submission, or whether an
empirical auction application should be treated as a prerequisite for an
upward journal target. I am not seeking another round of estimator tuning
before this decision.

\memoheading{Paper in one sentence}
When only auction maxima are observed, a structural WGAN can learn a coherent
global latent value distribution, but valid reserve-price inference requires
separate control of local CDF and density moments; cross-fitting and
orthogonality do not compensate for missing local identifying information.

\memoheading{What the paper contributes}
\begin{itemize}
  \item It embeds the auction order-statistic observation rule inside a
  bidder-level WGAN-GP, preserving symmetric independent private values before
  taking the observed maximum.
  \item It derives a cross-fitted Neyman-orthogonal score and an asymptotic
  linearity result for a fixed-bandwidth regularized reserve.
  \item It proves the required local nuisance rate for a training-fold empirical
  kernel learner under primitive fixed-bandwidth and local-overlap conditions.
  \item Nested Monte Carlo ablations isolate the failure of WGAN-based inference
  in local tail moments and motivate a hybrid global-WGAN/local-score estimator.
  \item External-validity designs identify a local-information boundary: the
  formal procedure is stable with three or five bidders but deteriorates with
  ten bidders when maxima rarely occur near the reserve.
\end{itemize}

\memoheading{Claim boundary}
\textbf{Formal claim:} valid inference for the fixed-bandwidth regularized
reserve when the stated nuisance-rate, overlap, and root conditions hold; these
conditions are verified for the empirical-local learner.\par
\textbf{Diagnostic evidence:} WGAN-GP global fit does not imply the local rate;
Richardson correction, residual-bias envelopes, and root-union intervals for
the exact Myerson reserve are finite-sample prototypes, not a uniform coverage
theorem.

\newpage
\memoheading{Key evidence}
\begin{itemize}
  \item Replacing WGAN score nuisances with training-fold empirical-local
  moments restores near-oracle RMSE and coverage in the baseline design.
  \item Fixed-bandwidth target coverage is 92.0--96.5 percent across baseline,
  heavy-tail, and mixture distributions with three or five bidders.
  \item With ten bidders and weak local support, coverage falls to roughly
  78 percent and multiple roots emerge.
  \item The stable $n^{-0.2}$ exact-target prototype reaches 96.5 percent
  coverage after a residual-bias envelope, but remains explicitly diagnostic.
\end{itemize}

\memoheading{Assumptions that should remain visible}
Symmetric independent private values; observed auction maxima; known bidder
count in the core design; local overlap around the reserve; and regular score
root/Jacobian behavior. The paper should not imply that orthogonality repairs
violations of these identifying conditions.

\memoheading{Three questions for the review}
\begin{enumerate}
  \item Is the local-information boundary plus the hybrid estimator a clear
  enough econometric contribution, or does the paper still read mainly as a
  WGAN application?
  \item Is IJCEE a sensible current-form target, or is the expected return high
  enough to first add an empirical bridge and target \emph{The Econometrics
  Journal} or \emph{Journal of Econometric Methods}?
  \item Which maintained auction assumption is most likely to concern a
  referee: symmetry/IPV, known bidder count, maxima-only observation, or local
  overlap?
\end{enumerate}

\memoheading{Suggested reading order}
Abstract and Introduction; Estimation and Inference; the local-nuisance and
external-validity simulation results; Conclusion; then the proof appendix as
needed. The identified and anonymous manuscripts, replication guide, and
archived results are synchronized in the project repository.

\end{document}
