\documentclass[11pt]{letter}
\usepackage[margin=0.82in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

\definecolor{heading}{RGB}{28,67,110}
\setlength{\parskip}{4pt}

\signature{Shunyu Hao}
\address{Shunyu Hao}
\date{July 19, 2026}

\begin{document}

\begin{letter}{Dr Giovanni Cerulli\\
Editor in Chief\\
\textit{International Journal of Computational Economics and Econometrics}}

\opening{Dear Dr Cerulli,}

Please consider the manuscript ``Semiparametric Inference for Myerson Reserve
Prices from Auction Maxima'' for publication in the \textit{International
Journal of Computational Economics and Econometrics}.

The paper studies inference on an economically important policy functional when
the latent bidder-value distribution is observed only through auction maxima.
It combines a structural Wasserstein generative adversarial network with
cross-fitting and a Neyman-orthogonal score. The central econometric result is
that global distributional fit is insufficient for inference when the reserve
depends on weakly observed local tail moments.

The manuscript makes three contributions:
\begin{itemize}
  \item it embeds the auction order-statistic observation rule inside a
  bidder-level structural generator;
  \item it provides formal fixed-bandwidth inference for a regularised reserve
  under primitive local nuisance and overlap conditions; and
  \item it uses Monte Carlo ablations and external-validity designs to identify
  the local-information boundary of the method and motivate a hybrid
  global-generator/local-score estimator.
\end{itemize}

The paper fits the journal's coverage of computational econometrics, Monte
Carlo simulation, robustness analysis, and software implementation. Its formal
fixed-bandwidth claim is kept separate from the diagnostic shrinking-bandwidth
procedures for the exact reserve. The submission uses simulated data only, has
no human participants, and includes a documented replication package with
deterministic integrity checks and archived result files.

The review manuscript is anonymised for double-blind evaluation and includes
conflicts-of-interest and AI-tool declarations. Thank you for considering the
paper.

\closing{Sincerely,}

\end{letter}
\end{document}
