\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}

\linespread{1.3}
\graphicspath{{figures/}{../output/figures/}}

\newtheorem{assumption}{Assumption}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}

\providecommand{\paperauthor}{Shunyu Hao}
\providecommand{\paperdisplayauthor}{\paperauthor}
\providecommand{\paperdate}{\today}
\providecommand{\replicationstatement}{All replication code, simulation designs,
and random seeds are available at
\url{https://github.com/Shunyu1001/WGAN-DML-Auctions}.}

\title{Semiparametric Inference for Myerson Reserve Prices\\
from Auction Maxima}
\author{\paperdisplayauthor}
\date{\paperdate}
\hypersetup{
  pdftitle={Semiparametric Inference for Myerson Reserve Prices from Auction Maxima},
  pdfauthor={\paperauthor},
  pdfsubject={Working paper},
  pdfkeywords={optimal auctions, reserve prices, auction maxima, double machine learning, semiparametric inference}
}

\begin{document}

\maketitle

\begin{abstract}
This paper studies inference for Myerson reserve prices when only auction maxima
are observed. Under symmetric independent private values, maxima identify the
latent value distribution, which is estimated globally by a structural
Wasserstein generative adversarial network with gradient penalty (WGAN-GP).
I derive a cross-fitted Neyman-orthogonal score for a fixed-bandwidth regularized
reserve. Primitive conditions give training-fold empirical kernel moments the
required $o_p(n^{-1/4})$ nuisance rate. Monte Carlo experiments show that good
global WGAN fit can coexist with inaccurate local tail moments and invalid
inference; an empirical-local nuisance restores near-nominal coverage. Across
valuation distributions, coverage remains stable with three or five bidders but
deteriorates with ten bidders when maxima rarely contain local identifying
information. Bias-corrected shrinking-bandwidth procedures improve exact-reserve
inference but remain diagnostic. The results support a hybrid workflow: use the
WGAN for global structural counterfactuals and local empirical moments for
reserve inference.
\end{abstract}

\noindent\textbf{Keywords:} optimal auctions; reserve prices; auction maxima;
order statistics; double machine learning; cross-fitting; Neyman orthogonality;
Wasserstein generative adversarial networks; semiparametric inference; Monte
Carlo simulation.\\
\textbf{JEL classification:} C14; C15; C45; D44.

\input{sections/introduction}
\input{sections/literature}
\input{sections/model}
\input{sections/identification}
\input{sections/estimation}
\input{sections/inference}
\input{sections/simulations}
\input{sections/empirical_application}
\input{sections/conclusion}
\input{sections/declarations}

\appendix
\input{sections/appendix}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
